### 2016-03-23 README.Rmd
Update README.Rmd

There are extensive details on using this package in the vignette that comes with the package and can be accessed using:

@@

>>>>

There are extensive details on using this package in the package vignette, which can be accessed once you install the package using:

@@

An uncompiled version of the vignette can be found, without having to install the package, [here](https://github.com/geanders/futureheatwaves/blob/master/vignettes/futureheatwaves.Rmd).
